### 2025-07-15 download-football-data.qmd
20250708 - track chunk execution times
20250715 - add acknowledgments and tweaks

nfl_standings_raw <- nflseedR::nfl_standings(
  nfl_schedules%>% filter(!is.na(result))) #read_csv("http://www.habitatring.com/standings.csv"); archived at: https://perma.cc/5QLN-VK7V
```

@@

TODO: Save/update data file in repo with the data generated from this code, and follow the data file through the rest of the book, updating code as necessary.

@@

We already load players' week-by-week statistics [above](#sec-downloadActualStats).
Nevertheless, we could compute players' weekly statistics from the play-by-play data using the following syntax:

TODO:

- Decide whether to use `calculate_stats()` from `nflfastR` [@R-nflfastR] or `load_player_stats()` from `nflreadr` [@R-nflreadr].
- Save/update data file in repo with the data generated from the relevant code, and follow the data file through the rest of the book, updating code as necessary.

>>>>

nfl_standings_raw <- nflseedR::nfl_standings(
  nfl_schedules %>% filter(!is.na(result))) #read_csv("http://www.habitatring.com/standings.csv"); archived at: https://perma.cc/5QLN-VK7V
```

@@

@@

We already load players' week-by-week statistics [above](#sec-downloadActualStats) using the `load_player_stats()` function from the `nflreadr` [@R-nflreadr] package.
Nevertheless, we could compute players' weekly statistics from the play-by-play data using the `calculate_stats()` function from the `nflfastR` [@R-nflfastR] package:

### 2025-07-15 index.qmd
20250715 - add acknowledgments and tweaks

I thank Dr. Benjamin Motz, who provided consultation and many helpful resources based on his fantasy football statistics class.
I also thank key members of [FantasyFootballAnalytics.net](http://fantasyfootballanalytics.net), including Val Pinskiy, Andrew Tungate, Dennis Andersen, and Adam Peterson, who helped develop and provide fantasy football-related resources and who helped sharpen my thinking about the topic.
In particular, Andrew Tungate made important additions to the [`ffanalytics` `R` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics] that were necessary for conducting a [bootstrap simulation](#sec-simulationProjectedPointsBootstrapping) of players' projected fantasy points.
I also thank Professor Patrick Carroll, who taught me the value of statistics for answering important questions.

>>>>

This work would not be possible without the important contributions of many people.
This book was made possible by the hard work of the package developers of the `nflverse` ecosystem of R packages, who made football data available, including Sebastian Carl, Ben Baldwin, Lee Sharpe, Tan Ho, and John Edwards.
I thank Dr. Benjamin Motz, who provided consultation and many helpful resources based on his fantasy football statistics class.
I also thank key members of [FantasyFootballAnalytics.net](http://fantasyfootballanalytics.net), including Val Pinskiy, Andrew Tungate, Dennis Andersen, and Adam Peterson, who helped develop and provide fantasy football-related resources and who helped sharpen my thinking about the topic.
In particular, Andrew Tungate made important additions to the [`ffanalytics` `R` package](https://github.com/FantasyFootballAnalytics/ffanalytics) [@R-ffanalytics] that were necessary for conducting a [bootstrap simulation](#sec-simulationProjectedPointsBootstrapping) of players' projected fantasy points.
I also thank Professor Patrick Carroll, who taught me the value of statistics for answering important questions.
